---
title: "STAT 140 Project" ## Change the title weekly according to the HW assignment number. 
author: "Hong Anh Nguyen" ## Change to your name. Use quotes! Also, put your collaboraters in parentheses. 
date: "`r format(Sys.Date(), '%m/%d/%Y')`" ## No need to change the date! This R command prints it out automatically.  
output: word_document ## Keep this as an html document, for now. 
---

```{r include = FALSE}   
knitr::opts_chunk$set(   # This is for later! Don't worry about it now. 
  echo = TRUE,           # Don't show code.
  warning = FALSE,       # Don't show warnings.
  message = FALSE,       # Don't show messages (less serious warnings).
  cache = FALSE,         # Set to TRUE to save results from last compilation.
  fig.align = "center"   # Center figures.
)
library(tidyverse)       # Load libraries you always use here.
library(tidymodels)
library(ggplot2)

#set.seed(27)             # Make random results reproducible
```

```{r cars}
prof_salary <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/carData/Salaries.csv") 
```


1. Rank

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = rank) +
  geom_bar()
```

```{r, echo = F}
summary(prof_salary$rank)
```

* Comment: This bar graph shows the distribution of professors' rank in a college in the U.S. According to the graph and the summary statistics, the number of Professors is nearly double the number of Assistant Professors and Associate Professors, which are 67 and 64, respectively. 


2. Discipline

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = discipline) +
  geom_bar()
```

```{r, echo = F}
summary(prof_salary$discipline)
```

* Comment: This bar graph gives information about the distribution of professors' discipline in a college in the U.S. According to the graph and the summary statistics, the number of Professors in “theoretical” departments (A) is approximately equal to the number of Professors in “applied” departments (B). 


3. Years since PhD

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = yrs.since.phd) +
  geom_histogram(binwidth = 5)
```

```{r, echo = F}
summary(prof_salary$yrs.since.phd)
```

* Comment: The distribution is centered around 22.31 with a median of 21 and ranges from about 1 to 56. It is a right-skewed, unimodal distribution with very few unusual values.

4. Years of service

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = yrs.service) +
  geom_histogram(binwidth = 5)
```

```{r, echo = F}
summary(prof_salary$yrs.service)
```

* Comment: The distribution is centered around 17.61 with a median of 16 and ranges from about 0 to 60. It is a right-skewed, bimodal distribution with some unusual values to the right of the graph.


5. Sex

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = sex) +
  geom_bar()
```

```{r, echo = F}
summary(prof_salary$sex)
```

* Comment: This bar graph describes the distribution of professors' sex in a college in the U.S. According to the graph and the summary statistics, the number of male faculty members far outweighs that of female faculty members. 


6. Salary

```{r, echo = F}
ggplot(data = prof_salary) + aes(x = salary) +
  geom_histogram(binwidth = 20000)
```

```{r, echo = F}
summary(prof_salary$salary)
```

* Comment: The distribution is centered around 113706 with a median of 107300 and ranges from about 57800 to 231545. It is a right-skewed, unimodal distribution with some unusual values after 200000.
