---
title: "STAT 140 Project" ## Change the title weekly according to the HW assignment number. 
author: "Hong Anh Nguyen" ## Change to your name. Use quotes! Also, put your collaboraters in parentheses. 
date: "`r format(Sys.Date(), '%m/%d/%Y')`" ## No need to change the date! This R command prints it out automatically.  
output: word_document ## Keep this as an html document, for now. 
---

```{r include = FALSE}   
knitr::opts_chunk$set(   # This is for later! Don't worry about it now. 
  echo = TRUE,           # Don't show code.
  warning = FALSE,       # Don't show warnings.
  message = FALSE,       # Don't show messages (less serious warnings).
  cache = FALSE,         # Set to TRUE to save results from last compilation.
  fig.align = "center"   # Center figures.
)
library(tidyverse)       # Load libraries you always use here.
library(tidymodels)
library(ggplot2)
library(kableExtra)
library(dplyr)

#set.seed(27)             # Make random results reproducible
```

```{r cars}
prof_salary <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/carData/Salaries.csv") 
```
  
* Categorical variable: discipline - a factor with levels A (“theoretical” departments) or B (“applied” departments).

a.
```{r}
ggplot(data = prof_salary, aes(x = yrs.service, y = salary, color = as.factor(discipline))) +
  geom_point() 
```

* The pattern of observations for A (“theoretical” departments) is a weak-moderate relationship that has some unusual values at the top of the graph. A linear model may not fit this graph.
* The pattern of observations for B (“applied” departments) is a fairly strong positive linear relationship that has some unusual values at the right bottom of the graph.

b. 
```{r, echo = F}
salary_model <- lm(data = prof_salary, salary ~ yrs.service + discipline)
summary(salary_model)$adj.r.squared
```

* 15.362% of the variation in the estimated academic salary can be explained by the number of years of service and the discipline.
* The adjusted R^2 is pretty low, which is consistent with the description of the scatterplot in part (a).

c.
```{r, echo = F}
salary_model <- lm(data = prof_salary, salary ~ yrs.service + discipline)
round(summary(salary_model)$coefficients, 3)
```

* On average, the salary for professors in a college in the U.S with discipline A ( (“theoretical” departments) is approximately $91335.832.
* For every professor in discipline B (“applied” departments), the expected salary will increase by about $13184.043.

d.
```{r, echo = F}
slope <- 13184.043
se_slope <- 2846.831
tstar <- qt(0.975, df = salary_model$df.residual)
```

```{r, echo = F}
slope - tstar*se_slope
slope + tstar*se_slope
```

* We are 95% confident that the slope for predicting the salary of professors from their discipline is between 7587.164 and 18780.92.
* Since this confidence interval does not contain 0, there is some evidence that there is a true, positive relationship between professors' salary and their discipline. 


